\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2015-09-10 doc/USER_MANUAL/06_fault_sources.tex

  There are a total of 13 columns.
  \begin{enumerate}
  \item{Column1} = Along strike distance(m)

  \item{Column2} = Along dip distances(m) The distance should be negative for points at depth

  \item{Column3} = Normal stress(Pa)

  \item{Column4} = Horizontal right-lateral shear stress(Pa)

  \item{Column5} = Vertical up-dip shear stress(Pa)

  \item{Column6} = $V_0$ value in RSF(m/s)

@@

  \item{Column11} = Initial slip velocity(m/s)

>>>>

  There are a total of 13 columns.
  \begin{enumerate}
  \item{Column1} = Along strike distance

  \item{Column2} = Along dip distances

  \item{Column3} = Normal stress(MPa)

  \item{Column4} = Horizontal right-lateral shear stress(MPa)

  \item{Column5} = Vertical up-dip shear stress(MPa)

  \item{Column6} = $V_0$ value in RSF

@@

  \item{Column11} = Initial slip velocity
